---
title: "LURN SI-29 synthetic data dashboard"
params:
  patient_id: 1
  show_table: FALSE
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{css}
.chart-wrapper{
    border: 2px solid black;
}
.value-box{
    border: 2px solid black;
}
.value-box .inner{
    padding: 0px 0px 0px 10px;
}
.value-box .value {
    font-size: 20px;
    margin: 0px;
}
.chart-title {
    font-size: 24px;
}

/* for the columns with combined plots and value boxes */
.plot-box-combined.value-box {
    height: 54px;
    text-align: left;
    border-top: none;
    border-radius: none;
}
.plot-box-combined.chart-wrapper{
    margin-bottom: 0px;
    border-bottom: none;
    border-radius: 0px;
}

/* the table needs scroll bars */
.scrollable-table .chart-shim{
    overflow-y: auto;
}

```


```{r global}
library(lurn)
library(ggplot2)
library(flexdashboard)
library(gt)
library(ggradar)
library(viridis)
library(dplyr)

# read in the patient database
syn <- read.csv("fromOneDrive/LURN_SI29_Synth_Final_NoFmt.csv", header = TRUE)
names(syn)[names(syn) == "Sex"] <- "SEX"
syn <- score_lurn_si_29(syn)
splom_vars <- c(
   "lurn_si_29_total_score", "lurn_si_29_incontinence_score",
   "lurn_si_29_pain_score", "lurn_si_29_voiding_score",
   "lurn_si_29_urgency_score", "lurn_si_29_nocturia_score",
   "lurn_si_29_bother")

# simplified dataframe for plots
splom_dat <- syn[c("ID", splom_vars)]
names(splom_dat)<- c("ID", "Total", "Incontinence", "Pain", "Voiding", "Urgency", "Nocturia", "Bother")
input_params <- list(
    patient_id = params$patient_id, 
    patient_row = which(splom_dat$ID == params$patient_id)[1]
)

# read in the time series file
syn_long <- read.csv("fromOneDrive/syn_long.csv", header = TRUE)
patient_cells <- list()
syn_long$ID <- factor(syn_long$ID)
syn_long_dat <- syn_long[c("ID", "Week", splom_vars)]
names(syn_long_dat)<- c("ID", "Week", "Total", "Incontinence", "Pain", "Voiding", "Urgency", "Nocturia", "Bother")



create_density_plot <- function(col, bw = "nrd0"){
    p <- splom_dat[[input_params$patient_row, col]]
    m <- median(splom_dat[[col]])
    lc <- ifelse(p > m, "#ff7518", "#2780E3")

    g <- ggplot(splom_dat, aes(x = .data[[col]])) +
        geom_density(fill = "lightgray", size = 3, bw = bw) + 
        geom_vline(xintercept = splom_dat[[input_params$patient_row, col]], color = lc, size = 5) +
        scale_x_continuous(expand = c(0,0)) +
        scale_y_continuous(expand = c(0,0)) +
        theme_classic() + 
        theme(
            text = element_text(size = 60),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank()
        )

    return(g)
}

create_hist_plot <- function(col, binwidth = 5){
    p <- splom_dat[[input_params$patient_row, col]]
    m <- median(splom_dat[[col]])
    lc <- ifelse(p > m, "#ff7518", "#2780E3")

    g <- ggplot(splom_dat, aes(x = .data[[col]])) +
        geom_histogram(fill = "lightgray", col = "black", size = 3, binwidth = binwidth) + 
        geom_vline(xintercept = splom_dat[[input_params$patient_row, col]], color = lc, size = 5) +
        scale_x_continuous(expand = c(0,0)) +
        scale_y_continuous(expand = c(0,0)) +
        theme_classic() + 
        theme(
            text = element_text(size = 60),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_blank()
        )

    return(g)
}


create_value_box <- function(col, ndec = 1){
    p <- splom_dat[[input_params$patient_row, col]]
    m <- median(splom_dat[[col]])
    pt <- format(round(p, ndec), nsmall = ndec)
    mt <- format(round(m, ndec), nsmall = ndec)
    return(valueBox(paste0(pt, ' (', mt, ')'), color = ifelse(p > m, "warning", "primary")))
}

create_full_table <- function(){
    # !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
    # can I color the borders dynamically to have blue and orange
    # !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

    # select the columns that we care about
    si_29_m_nms <- lurn_si_29_names("male")

    # create a table to this particular patient
    this_patient_row <- syn[input_params$patient_row, si_29_m_nms]

    # calculate the frequencies
    si29_prelim_freq_table <- t(apply(syn[si_29_m_nms], 2,
        function(x) table(factor(x, levels = 0:4), useNA = "always")))

    si29_prelim_prop_table <- prop.table(si29_prelim_freq_table, margin = 1)

    colnames(si29_prelim_prop_table) <- c("0", "1", "2", "3", "4", "Missing")

    # create a legend
    legend_dat <- data.frame(t(seq(0, 1, .2)))
    names(legend_dat) <- paste0(seq(0, 100, 20), "%")
    legend <- gt(legend_dat) %>%
        data_color(method = "numeric",
            palette = c("Greys"),
            domain = c(0, 1)) %>%
        fmt_number(pattern = "") %>%
        tab_header(title = "Legend") %>%
        opt_table_font(font = "Helvetica")


        
    # create the summary table
    si29_item_table <- as.data.frame(si29_prelim_prop_table) %>%
        gt(rownames_to_stub = TRUE) %>%
        tab_stubhead(label = "LURN SI-29 Item") %>%
        tab_options(table.background.color = "white") %>%
        data_color(
            method = "numeric",
            palette = c("Greys"),
            domain = c(0, 1)) |>
        fmt_number(
            decimals = 0,
            scale_by = 100,
            pattern = "{x}%") %>%
        fmt_number(
            rows = c(19, 21, 23, 28),
            columns = "4",
            pattern = "") %>%
        fmt_number(
            rows = 24,
            columns = c("2", "3", "4"),
            pattern = "") %>%
        cols_width(
            everything() ~ px(85)) %>%
        cols_width(
            1 ~ px(100)) 
            

    # highlight the responses from the patient
    for (cc in si_29_m_nms){
        patient_value <- this_patient_row[, cc]
        median_value <- median(syn[, cc], na.rm = TRUE)
        color <- ifelse(patient_value > median_value, "#ff7518", "#2780E3")

        si29_item_table <- si29_item_table %>%
            tab_style(
                style = list(
                    cell_borders(
                        sides = c("top", "bottom", "left", "right"),
                        color = color,
                        weight = px(4)
                    )
                ),
                locations = list(
                    cells_body(
                        columns = paste(patient_value),
                        rows = cc
                    )
                )
            )
    }

    return(
        list(
            "table" = si29_item_table,
            "legend" = legend
        )
    )

}

create_radar_plot <- function(weeks_to_use = c(0, 8, 16, 24)){

    # grab the desired patient and columns for radar plot
    patient_radar_data <- syn_long_dat[syn_long_dat$ID == input_params$patient_id, ]

    # take only the weeks that are requested
    patient_radar_data <- patient_radar_data[patient_radar_data$Week %in% weeks_to_use,]

    # rename column for ggradar
    names(patient_radar_data)[2] <- "Time"
    patient_radar_data$Time <- factor(patient_radar_data$Time)

    # remove the ID column
    patient_radar_data <- patient_radar_data[ , !names(patient_radar_data) == "ID"]


    # !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
    # I need to find a way to handle NaN values for the radar plot
    patient_radar_data[is.na(patient_radar_data)] = 0
    # !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

    g <- ggradar(patient_radar_data, grid.min = 0, grid.mid = 50, grid.max = 100, gridline.mid.colour = "grey",
        label.gridline.mid = TRUE,
        #group.colours = mako(length(weeks_to_use)),
        background.circle.colour = "lightgray",
        legend.title = "Weeks since procedure", 
        plot.extent.x.sf = 1.3,
        axis.label.size = 4, 
        grid.label.size = 3,
        group.point.size = 3,
        group.line.width = 1.5
        ) + 
        theme(
            text = element_text(size = 12), 
            legend.text = element_text(size = 7),
            # legend.position = c(0.75, -0.35),  
            legend.position = c(0.65, -0.35),  
            legend.justification = c(1, 0),
            plot.margin = grid::unit(c(-0.5, -0.1, -0.3, -0.1), "null")
        )  + 
        guides(color = guide_legend(nrow = 2)) 

    return(g)
}

create_line_plot <- function(col = "Total"){
    # !!!!!!!!!!!!!!!!!!!!!!!!!!!!!
    # needs a legend
    # !!!!!!!!!!!!!!!!!!!!!!!!!!!!!

    breaks <- seq(0, 24, 4)
    labels <- c("0\n(baseline)", "4", "8", "12", "16", "20", "24")

    line_df_input <- syn_long_dat[c("ID", "Week", col)]
    line_df_summary <- line_df_input %>%
        group_by(Week) %>%
        summarise(
            mean = mean(!!sym(col), na.rm = TRUE), 
            sd = sd(!!sym(col), na.rm = TRUE),
        )

    # loess regression
    span <- 0.75
    loess_mean <- loess(mean ~ Week, data = line_df_summary, span = span)
    loess_sd <- loess(sd ~ Week, data = line_df_summary, span = span)

    # new dataframe to plot
    Week <- seq(min(line_df_summary$Week), max(line_df_summary$Week), by = 0.1)
    line_df_plot <- data.frame(Week)
    line_df_plot$mean <- predict(loess_mean, line_df_plot)
    line_df_plot$hi <- pmin(line_df_plot$mean + predict(loess_sd, line_df_plot), 100)
    line_df_plot$lo <- pmax(line_df_plot$mean - predict(loess_sd, line_df_plot), 0)

    # grab the desired patient and columns for radar plot
    patient_line_data <- line_df_input[line_df_input$ID == input_params$patient_id, ]
    hi <- predict(loess_mean, patient_line_data) + predict(loess_sd, patient_line_data)
    patient_line_data$color <- ifelse(patient_line_data[col] > hi, "#ff7518", "#2780E3")

    g <- ggplot(data = line_df_plot, aes(x = Week)) + 
        geom_ribbon(aes(ymin = lo, ymax = hi), fill = "lightgray") +
        geom_line(aes(Week, mean), color = "black", size = 1.5) + 
        geom_line(aes(Week, hi), color = "black", linetype = "dashed", size = 1.5) + 
        geom_line(aes(Week, lo), color = "black", linetype = "dashed", size = 1.5) + 
        geom_point(data = patient_line_data, aes(Week, .data[[col]]), color = patient_line_data$color, size = 5) + 
        scale_y_continuous(paste(col, "Score"), limits = c(0, max(line_df_input[col]))) +
        scale_x_continuous("Weeks since procedure", breaks = breaks, labels = labels) + 
        theme_classic() + 
        theme(text = element_text(size = 20))

    return(g)
} 


```



Plots
=====================================   

Column {data-width=500}
-------------------------------------

### Total {class="plot-box-combined"}
    
```{r, fig.width = 10}
create_density_plot("Total")
```

### Total: Patient (Median) {class="plot-box-combined"}

```{r}
create_value_box("Total")
```



### Incontinence {class="plot-box-combined"}
    
```{r, fig.width = 10}
create_density_plot("Incontinence")
```

### Incontinence: Patient (Median) {class="plot-box-combined"}

```{r}
create_value_box("Incontinence")
```



### Pain {class="plot-box-combined"}
    
```{r, fig.width = 10}
create_density_plot("Pain")
```

### Pain: Patient (Median) {class="plot-box-combined"}

```{r}
create_value_box("Pain")
```



### Voiding {class="plot-box-combined"}
    
```{r, fig.width = 10}
create_density_plot("Voiding")
```

### Voiding: Patient (Median) {class="plot-box-combined"}

```{r}
create_value_box("Voiding")
```


Column {data-width=500}
-------------------------------------
   
### Urgency {class="plot-box-combined"}
    
```{r, fig.width = 10}
create_density_plot("Urgency")
```

### Urgency: Patient (Median) {class="plot-box-combined"}

```{r}
create_value_box("Urgency")
```



### Nocturia {class="plot-box-combined"}
    
```{r, fig.width = 10}
create_hist_plot("Nocturia", binwidth = 15)
```

### Nocturia: Patient (Median) {class="plot-box-combined"}

```{r}
create_value_box("Nocturia")
```



### Bother {class="plot-box-combined"}
    
```{r, fig.width = 10}
create_hist_plot("Bother", binwidth = 1)
# create_density_plot("Bother", bw = 0.5)
```

### Bother: Patient (Median) {class="plot-box-combined"}

```{r}
create_value_box("Bother")
```



### Empty Chart {class="plot-box-combined invisible"}
    
```{r, fig.width = 10}
```

### Empty Box {class="plot-box-combined invisible"}

```{r}
valueBox(0)
```

Column {data-width=700}
-------------------------------------

### Change Over Time
     
```{r, fig.width = 5}
create_line_plot(col = "Urgency")
```

### Radar Plot
     
```{r, fig.width = 5}
create_radar_plot()
```


Tables
=====================================  

Column {data-width=1050}
-------------------------------------

### Patient Scores Compared to Aggregate {class="scrollable-table"}

```{r}
tbl <- create_full_table()
tbl$table
```

<!-- used to click on the Tables panel so that I can rdner it -->
```{r results='asis'}
if (params$show_table) {
  js_code <- '<script>console.log("trying to show table");setTimeout(function() {var tablesPanel = document.querySelector(\'a[href="#tables"]\');tablesPanel.click();}, 100);</script>'
} else {
  js_code <- ''
}
cat(js_code)
```