---
title: "LURN SI-29 synthetic data dashboard"
params:
  patient_id: 3
  patient_week: 0
  show_table: FALSE
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    horizontal_layout: fill
---

```{css}
.chart-wrapper{
    border: 2px solid black;
}
.value-box{
    border: 2px solid black;
}
.value-box .inner{
    padding: 0px 0px 0px 10px;
}
.value-box .value {
    font-size: 20px;
    margin: 0px;
}
.chart-title {
    font-size: 24px;
}

/* for the columns with combined plots and value boxes */
.plot-box-combined.value-box {
    height: 54px;
    text-align: left;
    border-top: none;
    border-radius: none;
}
.plot-box-combined.chart-wrapper{
    margin-bottom: 0px;
    border-bottom: none;
    border-radius: 0px;
}

/* the table needs scroll bars */
.scrollable-table .chart-shim{
    overflow-y: auto;
}

```


```{r global}
library(lurn)
library(ggplot2)
library(flexdashboard)
library(gt)
library(dplyr)
library(tidyr)
library(cowplot)
library(magick)

# for renaming columns
splom_vars <- c(
   "lurn_si_29_total_score", 
   "lurn_si_29_incontinence_score",
   "lurn_si_29_pain_score", 
   "lurn_si_29_voiding_score",
   "lurn_si_29_urgency_score", 
   "lurn_si_29_nocturia_score",
   "lurn_si_29_bother")
symptoms <- c("Total", 
    "Incontinence", 
    "Pain", 
    "Voiding", 
    "Urgency", 
    "Nocturia", 
    "Bother"
)
splom_vars <- rev(splom_vars)
symptoms <- rev(symptoms)


# read in the time series file
syn_long <- read.csv("../data/syn_long.csv", header = TRUE)
patient_cells <- list()
syn_long$ID <- factor(syn_long$ID)
syn_long_dat <- syn_long[c("ID", "Week", splom_vars)]
names(syn_long_dat)<- append(c("ID", "Week"), symptoms)

# grab the appropriate week for the current symptoms plot
syn_week <- syn_long[syn_long$Week == params$patient_week, ]
syn_week_dat <- syn_long_dat[syn_long_dat$Week == params$patient_week, ]

# define the input_params (add patient_row)
input_params <- list(
    patient_id = params$patient_id, 
    patient_week = params$patient_week, 
    patient_row = which(syn_week_dat$ID == params$patient_id)[1]
)

# Function to rescale a column to a specific range
# what about NaN??
rescale_to_range <- function(x, new_min, new_max) {
    scaled <- (x - min(x, na.rm = TRUE))/(max(x, na.rm = TRUE) - min(x, na.rm = TRUE))  # Scale to range [0, 1]
    scaled_rescaled <- ifelse(is.na(x), 0, scaled*(new_max - new_min) + new_min)  # Rescale to new range
    return(scaled_rescaled)
}
syn_week_dat$Bother <- rescale_to_range(syn_week_dat$Bother, 0, 100)
syn_long_dat$Bother <- rescale_to_range(syn_long_dat$Bother, 0, 100)


create_full_table <- function(){
    # Code mostly from Jamie Griffith

   # the questions
    q_vec <- c("Loss of bladder Control",
        "Urine leakage",
        "Urine leakage from laughing, coughing, etc.",
        "Urine leakage during activities",
        "Urine leakage from walking",
        "Urine leakage at night",
        "Pain/discomfort with bladder filling",
        "Pain/discomfort with full bladder", 
        "Pain/discomfort during Urination",
        "Pain/discomfort after urination",
        "Need to push for Urination",
        "Delay in urination",
        "Repeated stops in urine flow",
        "Slow/Weak urine flow",
        "Trickle/dribble after urination",
        "Sudden need to urinate",
        "Sudden need to urinate with potential leakage",
        "How difficult was it to wait more than a few minutes?",
        "Times awakened to urinate per night",
        "Frequency of nights awakened to urinate",
        "Number of daytime urinations",
        "Time between daytime urinations",
        "Strength of nighttime urge to urinate",
        "Constant need to urinate",
        "Bladder not empty after urination",
        "Urine dribble after voiding",
        "Splitting/spraying of urine stream",
        "Bothered from urinary symptoms")





    # select the columns that we care about
    si_29_m_nms <- lurn_si_29_names("male")

    # create a table for this particular patient
    this_patient_row <- syn_week[input_params$patient_row, si_29_m_nms]

    # calculate the frequencies
    si29_prelim_freq_table <- t(apply(syn_week[si_29_m_nms], 2,
        function(x) table(factor(x, levels = 0:4), useNA = "always")))

    si29_prelim_prop_table <- prop.table(si29_prelim_freq_table, margin = 1)

    colnames(si29_prelim_prop_table) <- c("0", "1", "2", "3", "4", "Missing")


    si29_prop_table <- cbind(`Question: Short description` = q_vec,
                            as.data.frame(si29_prelim_prop_table))

    si29_item_table <- si29_prop_table %>%
        gt(rownames_to_stub = TRUE) %>%
        tab_stubhead(label = md("**LURN SI-29 Item**")) %>%
        tab_spanner(
            label = "Response options (0-4): Higher numbers mean higher severity",
            columns = c("0", "1", "2", "3", "4", "Missing")) %>%
        tab_options(table.background.color = "white") %>%
        data_color(
            columns = c("0", "1", "2", "3", "4", "Missing"),
            method = "numeric",
            palette = c("Greys"),
            domain = c(0, 1)) %>%
        fmt_number(
            columns = c("0", "1", "2", "3", "4", "Missing"),
            decimals = 0,
            scale_by = 100,
            pattern = "{x}%") %>%
        fmt_number(
            rows = c(19, 21, 23, 28),
            columns = "4",
            pattern = "") %>%
        fmt_number(
            rows = 24,
            columns = c("2", "3", "4"),
            pattern = "") %>%
        cols_width(
            everything() ~ px(80)) %>%
        cols_width(
            1 ~ px(150)) %>%
        cols_width(
            2 ~ px(300)) %>%
        cols_width(
            8 ~ px(100)) %>%
        tab_header(title = md(
            "**Figure 1: LURN SI-29: Percentages of response values**"),
            subtitle = 
            "Synthetic data: Darker gray corresponds to higher percentages") %>%
        tab_footnote(footnote = 
            "For items SI29_Q19, SI29_Q21, SI29_Q23, SI29_Q24, and SI29_Q28, blank cells are not possible response values") %>%
        tab_source_note(source_note = paste0("Data are synthetic for testing and simulation purposes. N = ",  length(syn_week$ID))) %>%
        opt_table_font(font = "Helvetica") %>%
        tab_row_group(label = md("**Section F: Additional symptoms and bother**"),
                        rows = c("SI29_Q21", "SI29_Q22", "SI29_Q23", "SI29_Q24",
                                "SI29_Q25", "SI29_Q26", "SI29_Q27b",
                                "SI29_Q28")) %>%
        tab_row_group(label = md("**Section E: Nocturia**"),
                        rows = c("SI29_Q19", "SI29_Q20")) %>% 
        tab_row_group(label = md("**Section D: Urgency**"),
                        rows = c("SI29_Q16", "SI29_Q17", "SI29_Q18")) %>%
        tab_row_group(label = md("**Section C: Voiding difficulty**"),
                        rows = c("SI29_Q11", "SI29_Q12", "SI29_Q13",
                                "SI29_Q14", "SI29_Q15")) %>%
        tab_row_group(label = md("**Section B: Pain**"),
                        rows = c("SI29_Q7", "SI29_Q8", "SI29_Q9", "SI29_Q10")) %>%
        tab_row_group(label = md("**Section A: Incontinence**"),
                        rows = c("SI29_Q1", "SI29_Q2", "SI29_Q3",
                                "SI29_Q4", "SI29_Q5", "SI29_Q6")) %>%
        cols_label(`Question: Short description` = 
                    md("**Question: Short description**"))

    # highlight the responses from the patient

    # Define a custom color palette
    custom_palette <- c("#2780E3", "black", "#ff7518")
    # Create a color ramp function using the custom palette
    color_ramp <- colorRampPalette(custom_palette)

    # iterate through the questions
    for (cc in si_29_m_nms){
        patient_value <- this_patient_row[, cc]
        if (!is.nan(patient_value) & !is.na(patient_value)){
            median_value <- median(syn_week[, cc], na.rm = TRUE)
            Percentile_16 = quantile(syn_week[, cc], probs = 0.16, na.rm = TRUE)
            Percentile_84 = quantile(syn_week[, cc], probs = 0.84, na.rm = TRUE)
            width <- Percentile_84 - Percentile_16
            # what should I do with width == 0 ??!!
            if (width == 0) width <- 1.

            # Calculate the color value based on (patient_value - median_value) / width
            color_value <- (patient_value - median_value)/width
            color_value <- pmin(pmax(color_value, -1), 1)

            # Map color value to the custom palette
            color <- color_ramp(100)[findInterval(color_value, seq(-1, 1, length.out = 100))]
            si29_item_table <- si29_item_table %>%
                tab_style(
                    style = list(
                        cell_borders(
                            sides = c("top", "bottom", "left", "right"),
                            color = color,
                            weight = px(4)
                        )
                    ),
                    locations = list(
                        cells_body(
                            columns = paste(patient_value),
                            rows = cc
                        )
                    )
                )
        }
    }

    # create the legend for the reference population
    legend_dat <- data.frame(t(seq(0, 1, .2)))
    names(legend_dat) <- paste0(seq(0, 100, 20), "%")
    legend <- gt(legend_dat) %>%
        data_color(method = "numeric",
            palette = c("Greys"),
            domain = c(0, 1)) %>%
        fmt_number(pattern = "") %>%
        tab_header(title = "Population Values Legend") %>%
        opt_table_font(font = "Helvetica")

    # create the legend for the patient
    legend_patient_dat <- data.frame(t(seq(-1, 1, .25)))
    names(legend_patient_dat) <- seq(-1, 1, 0.25)
    legend_patient <- gt(legend_patient_dat) %>%
        data_color(method = "numeric",
            palette = custom_palette,
            domain = c(-1, 1)) %>%
        fmt_number(pattern = "") %>%
        tab_header(title = "Patient Values Legend: (patient_value - median)/width") %>%
        opt_table_font(font = "Helvetica")


    return(
        list(
            "table" = si29_item_table,
            "comparison_legend" = legend,
            "patient_legend" = legend_patient
        )
    )

}


create_current_week_summary_bar_chart <- function(){

    # create a summary for each of the columns for all patients as a comparison
    df <- select(syn_week_dat, -c(ID, Week))
    summary_df <- data.frame(
        Median = apply(df, 2, median, na.rm = TRUE),
        Percentile_16 = apply(df, 2, function(x) quantile(x, probs = 0.16, na.rm = TRUE)),
        Percentile_84 = apply(df, 2, function(x) quantile(x, probs = 0.84, na.rm = TRUE))
    )

    # Add a row for the full 1sigma width
    summary_df$Width <- summary_df$Percentile_84 - summary_df$Percentile_16

    # what should we do if width == 0??
    summary_df$Width[summary_df$Width == 0] <- 1.

    # add the symptoms in the correct order
    summary_df$Symptom <- factor(rownames(summary_df), levels = symptoms)

    # get the patient data for the bar chart
    df_patient <- select(syn_week_dat[input_params$patient_row, ], -c(ID, Week))
    p <- as.data.frame(t(df_patient))
    summary_df$Value <- p[, 1]

    # Define a custom color palette
    custom_palette <- c("#2780E3", "white", "#ff7518")

    # for labelling (so that I can match the size of the other plot)
    breaks <- seq(0, 100, 20)
    labels <- c("0\n", "20", "40", "60", "80", "100")

    # get the maximum value to define the axis limits
    max_value <- max(unlist(summary_df[sapply(summary_df, is.numeric)]), na.rm = TRUE)

    main <- ggplot(summary_df[(summary_df$Symptom != "Total"),], aes(x = Symptom, y = Value, fill = (Value - Median)/Width)) +
        scale_y_continuous("", breaks = breaks, labels = labels, limits = c(0, max_value)) +
        geom_bar(stat = "identity", fill = "white", color = "black", size = 1.5) + 
        geom_bar(stat = "identity") + 
        scale_fill_gradient2(
            low = custom_palette[1], 
            mid = custom_palette[2], 
            high = custom_palette[3],
            midpoint = 0, 
            limits = c(-1,1),
            oob = scales::squish
        ) +    
        geom_errorbar(aes(y = NULL, ymin = Median, ymax = Median), width = 0.75, color = "darkgray", size = 3) +
        facet_grid(Symptom ~ ., 
            scales = "free_y", 
            switch = "both"
        ) +
        coord_flip() +
        guides(fill = FALSE) +
        theme_bw() +
        xlab("") + 
        theme(
            panel.spacing = unit(0, "lines"),
            strip.text = element_text(size = 0, margin = margin(0,0,0,0)),
            plot.margin = margin(0.7, 0.09, 0.85, 5, "cm"),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
         ) 

    total <- ggplot(summary_df[(summary_df$Symptom == "Total"),], aes(x = Symptom, y = Value, fill = (Value - Median)/Width)) +
        scale_x_discrete(breaks = "", labels = "") +
        scale_y_continuous("Symptom level", breaks = breaks, labels = labels, limits = c(0, max_value)) +
        geom_bar(stat = "identity", fill = "white", color = "black", size = 1.5) + 
        geom_bar(stat = "identity") + 
        scale_fill_gradient2(
            low = custom_palette[1], 
            mid = custom_palette[2], 
            high = custom_palette[3],
            midpoint = 0, 
            limits = c(-1,1),
            oob = scales::squish
        ) +    
        geom_errorbar(aes(y = NULL, ymin = Median, ymax = Median), width = 0.75, color = "darkgray", size = 3) +
        facet_grid(Symptom ~ ., 
            scales = "free_y", 
            switch = "both"
        ) +
        coord_flip() +
        guides(fill = FALSE) +
        theme_bw() +
        xlab("") + 
        theme(
            strip.text = element_text(size = 0, margin = margin(0,0,0,0)),
            plot.margin = margin(0., 0.09, 0.25, 5, "cm"),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
         ) 

    g <- plot_grid(main, total, 
        labels = c('Symptom', 'Total'), 
        rel_heights = c(length(symptoms) - 1, 1.4),
        label_y = c(1.01, 1.25),
        label_x = c(0.25,0.37),
        ncol = 1,
        align = "v",
        axis = "b"
    )


    return(g)
}

create_time_series_line_plot <- function(){

    # there may be a more streamlined way to do this, but I don't know it!
    median_values <- syn_long_dat %>%
        group_by(Week) %>%
        summarize(across(-c(ID), median, na.rm = TRUE))
    median_values_t <- median_values %>%
        pivot_longer(cols = -c(Week),
            names_to = "Symptom",
            values_to = "Median")

    Q1_values <- syn_long_dat %>%
        group_by(Week) %>%
        summarize(across(-c(ID), ~ quantile(., 0.16, na.rm = TRUE)))
    Q1_values_t <- Q1_values %>%
        pivot_longer(cols = -c(Week),
            names_to = "Symptom",
            values_to = "Q1")

    Q3_values <- syn_long_dat %>%
        group_by(Week) %>%
        summarize(across(-c(ID), ~ quantile(., 0.84, na.rm = TRUE)))
    Q3_values_t <- Q3_values %>%
        pivot_longer(cols = -c(Week),
            names_to = "Symptom",
            values_to = "Q3")

    patient_data <- select(syn_long_dat[syn_long_dat$ID == input_params$patient_id, ], -ID)
    patient_data_t <- patient_data %>%
        pivot_longer(cols = -c(Week),
            names_to = "Symptom",
            values_to = "Value")

    merged_df <- merge(median_values_t, Q1_values_t, by = c("Week", "Symptom")) %>%
        merge(Q3_values_t, by = c("Week", "Symptom")) %>%
        merge(patient_data_t, by = c("Week", "Symptom"))
        

    # Add a row for the full 1sigma width
    merged_df$Width <- merged_df$Q3 - merged_df$Q1
    # what should I do with width == 0 ??!!
    merged_df$Width[merged_df$Width == 0] <- 1.

    # set the symptoms as a factor and in the correct order
    merged_df$Symptom <- factor(merged_df$Symptom, levels = symptoms)

    # omit the rows with nan values??
    merged_df_clean_limit_week <- na.omit(merged_df[merged_df$Week <= input_params$patient_week, ])

    # custom color palette
    custom_palette <- c("#2780E3", "white", "#ff7518")

    # for labelling
    breaks <- seq(0, 24, 4)
    labels <- c("0\n(baseline)", "4", "8", "12", "16", "20", "24")
    labels2 <- c("0", "4", "8", "12", "16", "20", "24")

    # function to calculate custom breaks
    custom_breaks <- function(data, n_breaks = 4, tol = 0.5) {
        # Calculate breaks based on data range
        min_value <- min(data)
        max_value <- max(data)
        breaks <- pretty(c(min_value, max_value), n = n_breaks)
        diff <- breaks[2] - breaks[1]
        top_diff <- max_value - breaks[length(breaks)]
        if (abs(top_diff/diff) > tol) {
            breaks <- breaks[1:(length(breaks) - 1)]
            if (top_diff < 0){
                breaks <- breaks[1:(length(breaks) - 1)]
            }
        }
        return(breaks)
    }

    main <- ggplot(merged_df[(merged_df$Symptom != "Total"),], aes(x = Week, y = Median)) +
        geom_line(color = "darkgray", linetype = "dashed", size = 1.5) +
        geom_line(data = merged_df_clean_limit_week[(merged_df_clean_limit_week$Symptom != "Total"),], aes(y = Value)) +
        geom_point(data = merged_df_clean_limit_week[(merged_df_clean_limit_week$Symptom != "Total"),], aes(y = Value, fill = (Value - Median)/Width), shape = 21, color = "black", size = 4, stroke = 1.5) + 
        scale_fill_gradient2(
            low = custom_palette[1], 
            mid = custom_palette[2], 
            high = custom_palette[3],
            midpoint = 0, 
            limits = c(-1, 1),
            oob = scales::squish
        ) +   
        facet_grid(Symptom ~ ., 
            scales = "free_y", 
            switch = "both",
        ) + 
        scale_x_continuous("", breaks = breaks, labels = labels2, limits = c(0, 24)) + 
        scale_y_continuous("Symptom level", expand = expansion(mult = c(0.1, 0.25)),
            breaks = function(x) {
                return(custom_breaks(x))
            },
            position = "right"
        ) +
        expand_limits(x = c(-1, 26)) + 
        ylab("") + 
        # theme_void() + 
        guides(fill = FALSE) +
        theme_bw() + 
        theme(
            panel.spacing = unit(0, "lines"),
            strip.text = element_text(size = 0, margin = margin(0,0,0,0)),
            plot.margin = margin(0.7, 7, 1.2, 0.1, "cm"),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.title.y.right = element_text(margin = margin(l = 10))
        )  

    total <- ggplot(merged_df[(merged_df$Symptom == "Total"),], aes(x = Week, y = Median)) +
        geom_line(color = "darkgray", linetype = "dashed", size = 1.5) +
        geom_line(data = merged_df_clean_limit_week[(merged_df_clean_limit_week$Symptom == "Total"),], aes(y = Value)) +
        geom_point(data = merged_df_clean_limit_week[(merged_df_clean_limit_week$Symptom == "Total"),], aes(y = Value, fill = (Value - Median)/Width), shape = 21, color = "black", size = 4, stroke = 1.5) + 
        scale_fill_gradient2(
            low = custom_palette[1], 
            mid = custom_palette[2], 
            high = custom_palette[3],
            midpoint = 0, 
            limits = c(-1, 1),
            oob = scales::squish
        ) +   
        facet_grid(Symptom ~ ., 
            scales = "free_y", 
            switch = "both",
        ) + 
        scale_x_continuous("Weeks since procedure", breaks = breaks, labels = labels, limits = c(0, 24)) + 
        scale_y_continuous("", expand = expansion(mult = c(0.1, 0.25)),
            breaks = function(x) {
                return(custom_breaks(x))
            },
            position = "right"
        ) +
        expand_limits(x = c(-1, 26)) + 
        ylab("") + 
        # theme_void() + 
        guides(fill = FALSE) +
        theme_bw() + 
        theme(
            strip.text = element_text(size = 0, margin = margin(0,0,0,0)),
            plot.margin = margin(0., 7, 0.25, 0.1, "cm"),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.title.y.right = element_text(margin = margin(l = 10))
        ) 

    g <- plot_grid(main, total, 
        rel_heights = c(length(symptoms) - 1, 1.4),
        ncol = 1,
        align = "v",
        axis = "b"
    )

    # create another plot just for the legend (not sure there's a simpler way to do this!)
    breaks <- c(-1, 1)
    labels <- c("Below\nreference\npopulation", "Above\nreference\npopulation")
    g_legend <- ggplot(merged_df, aes(x = Week, y = Median)) +
        geom_line(color = "darkgray", linetype = "dashed", size = 1.5) +
        geom_line(data = merged_df_clean_limit_week, aes(y = Value)) +
        geom_point(data = merged_df_clean_limit_week, aes(y = Value, fill = (Value - Median)/Width), shape = 21, color = "black", size = 4, stroke = 1.5) + 
        scale_fill_gradient2(
            low = custom_palette[1], 
            mid = custom_palette[2], 
            high = custom_palette[3],
            midpoint = 0, 
            limits = c(-1, 1),
            oob = scales::squish,
            breaks = breaks,
            labels = labels
        ) +    
         guides(
            fill = guide_colorbar(
                title = "",#Scaled offset from median of reference population",
                title.position = "bottom",
                title.hjust = 0.5,
                title.vjust = 0,
                label.position = "bottom"
            )
        ) + 
        theme_bw() + 
        theme(
            legend.position = "bottom",           
            legend.key.width = unit(1, "cm"),
            legend.title.align = 0.5,
            legend.margin = margin(margin(10,0,0,0,"cm")),
            legend.title = element_text(size = 9), 
            legend.text = element_text(size = 12, color = "#555555")
        )   


    legend <- cowplot::get_legend(g_legend)
    

    return(
        list(
            "plot" = g,
            "legend" = legend
        )
    )
}

annotate_img <- function(p, acolor){
    # save the image and then read it back in so that I can annotate it more easily!
    tmp <- tempfile("image0", fileext = ".png")
    ggsave(tmp, p, width = 12, height = 8)
    img <- image_read(tmp)  %>%
        # left plot label
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = 90, location = "+780+1650") %>%
        image_annotate("Plots on the left show\nyour present symptoms\nin color-filled rectangles", size = 60, color = acolor,
            boxcolor = "transparent", degrees = 0, location = "+170+1640", font = 'Times') %>%
        # right plot label
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = -90, location = "+2800+1800") %>%
        image_annotate("Plots on the right show\nyour symptoms over time\nin color-filled circles", size = 60, color = acolor,
            boxcolor = "transparent", degrees = 0, location = "+2890+1640", font = 'Times')  %>%
        # left plot reference (TODO - link x position to actual total reference value)
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = 30, location = "+940+1750")  %>%
        image_annotate("Reference population", size = 60, color = acolor,
            boxcolor = "transparent", degrees = 0, location = "+500+1900", font = 'Times')  %>%      
        # right plot reference (TODO - link x position to actual total reference value)
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = -30, location = "+2460+1850")  %>%
        image_annotate("Reference population", size = 60, color = acolor,
            boxcolor = "transparent", degrees = 0, location = "+2580+1900", font = 'Times')  %>%      
        # left plot explanation (TODO - link x position to actual patient value and automatic text)
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = 210, location = "+1190+1660")  %>%
        image_annotate("Your total score is nearly\nthe same as the reference population", size = 60, color = acolor,
            boxcolor = "transparent", degrees = 0, location = "+1180+1480", font = 'Times')  %>%
        # left plot explanation (TODO - link x position to actual patient value and automatic text)
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = 210, location = "+2330+1750")  %>%
        image_annotate("Your total score has decreased\nsince your last visit", size = 60, color = acolor,
            boxcolor = "transparent", degrees = 0, location = "+2330+1480", font = 'Times') 

    return(img) 
}
```



Plots
=====================================   

Row {data-height=800, id="chart1"}
-------------------------------------

### Symptoms Summary for Patient `r params$patient_id` at Week `r params$patient_week`
    
```{r, fig.width = 10, fig.height = 10}
bar_chart <- create_current_week_summary_bar_chart()
line_plot <- create_time_series_line_plot()

g <- plot_grid(bar_chart, line_plot$plot, ncol = 2, align = "h", rel_widths = c(0.49,0.51), axis = "l")
p <- plot_grid(g, line_plot$legend, ncol = 1, rel_heights = c(1, 0.2))


img <- annotate_img(p, "#a200aa")
image_trim(img)

```


<!-- 
Row {data-height=125}
-------------------------------------

### Description
The figures above show results from survey(s) you filled out recording the level of your symptoms at each doctor visit.  

The panels on the left show your current symptoms in color-filled rectangles compared to a reference population shown in gray lines. The panels on the right show your symptoms over time in color-filled circles compared to the same reference population shown in gray dashed lines. 

In all panels, the color indicates how your symptom level compares with that of the reference population, with blue being lower and orange being higher than the reference population, as indicated by the colorbar at the bottom.   
-->



Tables
=====================================  

Row {data-width=1050}
-------------------------------------

### Patient Scores Compared to Aggregate for Patient `r params$patient_id` at Week `r params$patient_week` {class="scrollable-table"}

```{r}
tbl <- create_full_table()
tbl$table
tbl$comparison_legend
tbl$patient_legend
```

<!-- used to click on the Tables panel so that I can render it -->
```{r results='asis'}
if (params$show_table) {
  js_code <- '<script>console.log("trying to show table");setTimeout(function() {var tablesPanel = document.querySelector(\'a[href="#tables"]\');tablesPanel.click();}, 100);</script>'
} else {
  js_code <- ''
}
cat(js_code)
```