---
title: "LURN SI-29 synthetic data dashboard"
params:
    patient_id: 3
    patient_week: 0
    show_table: FALSE
    annotate_plot: FALSE
output: 
    flexdashboard::flex_dashboard:
        orientation: rows
        vertical_layout: fill
        horizontal_layout: fill
---

```{css}
.chart-wrapper{
    border: 2px solid black;
}
.value-box{
    border: 2px solid black;
}
.value-box .inner{
    padding: 0px 0px 0px 10px;
}
.value-box .value {
    font-size: 20px;
    margin: 0px;
}
.chart-title {
    font-size: 24px;
}

/* for the columns with combined plots and value boxes */
.plot-box-combined.value-box {
    height: 54px;
    text-align: left;
    border-top: none;
    border-radius: none;
}
.plot-box-combined.chart-wrapper{
    margin-bottom: 0px;
    border-bottom: none;
    border-radius: 0px;
}

/* the table needs scroll bars */
.scrollable-table .chart-shim{
    overflow-y: auto;
}

```


```{r global}
library(lurn)
library(ggplot2)
library(flexdashboard)
library(gt)
library(dplyr)
library(tidyr)
library(cowplot)
library(magick)
library(ggnewscale)

# for renaming columns
splom_vars <- c(
   "lurn_si_29_total_score", 
   "lurn_si_29_incontinence_score",
   "lurn_si_29_pain_score", 
   "lurn_si_29_voiding_score",
   "lurn_si_29_urgency_score", 
   "lurn_si_29_nocturia_score",
   "lurn_si_29_bother")
symptoms <- c("Total", 
    "Incontinence", 
    "Pain", 
    "Voiding", 
    "Urgency", 
    "Nocturia", 
    "Bother"
)
splom_vars <- rev(splom_vars)
symptoms <- rev(symptoms)


# read in the time series file
syn_long <- read.csv("../data/syn_long.csv", header = TRUE)
patient_cells <- list()
syn_long$ID <- factor(syn_long$ID)
syn_long_dat <- syn_long[c("ID", "Week", splom_vars)]
names(syn_long_dat) <- append(c("ID", "Week"), symptoms)

# grab the appropriate week for the current symptoms plot
syn_week <- syn_long[syn_long$Week == params$patient_week, ]
syn_week_dat <- syn_long_dat[syn_long_dat$Week == params$patient_week, ]

# define the input_params (add patient_row)
input_params <- list(
    patient_id = params$patient_id, 
    patient_week = params$patient_week, 
    patient_row = which(syn_week_dat$ID == params$patient_id)[1]
)

# Rescale bother to 0-100
syn_week_dat$Bother <- syn_week_dat$Bother/3*100
syn_long_dat$Bother <- syn_long_dat$Bother/3*100


create_full_table <- function(){
    # Code mostly from Jamie Griffith

   # the questions
    q_vec <- c("Loss of bladder Control",
        "Urine leakage",
        "Urine leakage from laughing, coughing, etc.",
        "Urine leakage during activities",
        "Urine leakage from walking",
        "Urine leakage at night",
        "Pain/discomfort with bladder filling",
        "Pain/discomfort with full bladder", 
        "Pain/discomfort during Urination",
        "Pain/discomfort after urination",
        "Need to push for Urination",
        "Delay in urination",
        "Repeated stops in urine flow",
        "Slow/Weak urine flow",
        "Trickle/dribble after urination",
        "Sudden need to urinate",
        "Sudden need to urinate with potential leakage",
        "How difficult was it to wait more than a few minutes?",
        "Times awakened to urinate per night",
        "Frequency of nights awakened to urinate",
        "Number of daytime urinations",
        "Time between daytime urinations",
        "Strength of nighttime urge to urinate",
        "Constant need to urinate",
        "Bladder not empty after urination",
        "Urine dribble after voiding",
        "Splitting/spraying of urine stream",
        "Bothered from urinary symptoms")





    # select the columns that we care about
    si_29_m_nms <- lurn_si_29_names("male")

    # create a table for this particular patient
    this_patient_row <- syn_week[input_params$patient_row, si_29_m_nms]

    # calculate the frequencies
    si29_prelim_freq_table <- t(apply(syn_week[si_29_m_nms], 2,
        function(x) table(factor(x, levels = 0:4), useNA = "always")))

    si29_prelim_prop_table <- prop.table(si29_prelim_freq_table, margin = 1)

    colnames(si29_prelim_prop_table) <- c("0", "1", "2", "3", "4", "Missing")


    si29_prop_table <- cbind(`Question: Short description` = q_vec,
                            as.data.frame(si29_prelim_prop_table))

    si29_item_table <- si29_prop_table %>%
        gt(rownames_to_stub = TRUE) %>%
        tab_stubhead(label = md("**LURN SI-29 Item**")) %>%
        tab_spanner(
            label = "Response options (0-4): Higher numbers mean higher severity",
            columns = c("0", "1", "2", "3", "4", "Missing")) %>%
        tab_options(table.background.color = "white") %>%
        data_color(
            columns = c("0", "1", "2", "3", "4", "Missing"),
            method = "numeric",
            palette = c("Greys"),
            domain = c(0, 1)) %>%
        fmt_number(
            columns = c("0", "1", "2", "3", "4", "Missing"),
            decimals = 0,
            scale_by = 100,
            pattern = "{x}%") %>%
        fmt_number(
            rows = c(19, 21, 23, 28),
            columns = "4",
            pattern = "") %>%
        fmt_number(
            rows = 24,
            columns = c("2", "3", "4"),
            pattern = "") %>%
        cols_width(
            everything() ~ px(80)) %>%
        cols_width(
            1 ~ px(150)) %>%
        cols_width(
            2 ~ px(300)) %>%
        cols_width(
            8 ~ px(100)) %>%
        tab_header(title = md(
            "**Figure 1: LURN SI-29: Percentages of response values**"),
            subtitle = 
            "Synthetic data: Darker gray corresponds to higher percentages") %>%
        tab_footnote(footnote = 
            "For items SI29_Q19, SI29_Q21, SI29_Q23, SI29_Q24, and SI29_Q28, blank cells are not possible response values") %>%
        tab_source_note(source_note = paste0("Data are synthetic for testing and simulation purposes. N = ",  length(syn_week$ID))) %>%
        opt_table_font(font = "Helvetica") %>%
        tab_row_group(label = md("**Section F: Additional symptoms and bother**"),
                        rows = c("SI29_Q21", "SI29_Q22", "SI29_Q23", "SI29_Q24",
                                "SI29_Q25", "SI29_Q26", "SI29_Q27b",
                                "SI29_Q28")) %>%
        tab_row_group(label = md("**Section E: Nocturia**"),
                        rows = c("SI29_Q19", "SI29_Q20")) %>% 
        tab_row_group(label = md("**Section D: Urgency**"),
                        rows = c("SI29_Q16", "SI29_Q17", "SI29_Q18")) %>%
        tab_row_group(label = md("**Section C: Voiding difficulty**"),
                        rows = c("SI29_Q11", "SI29_Q12", "SI29_Q13",
                                "SI29_Q14", "SI29_Q15")) %>%
        tab_row_group(label = md("**Section B: Pain**"),
                        rows = c("SI29_Q7", "SI29_Q8", "SI29_Q9", "SI29_Q10")) %>%
        tab_row_group(label = md("**Section A: Incontinence**"),
                        rows = c("SI29_Q1", "SI29_Q2", "SI29_Q3",
                                "SI29_Q4", "SI29_Q5", "SI29_Q6")) %>%
        cols_label(`Question: Short description` = 
                    md("**Question: Short description**"))

    # highlight the responses from the patient

    # Define a custom color palette
    custom_palette <- c("#2780E3", "black", "#ff7518")
    # Create a color ramp function using the custom palette
    color_ramp <- colorRampPalette(custom_palette)

    # iterate through the questions
    for (cc in si_29_m_nms){
        patient_value <- this_patient_row[, cc]
        if (!is.nan(patient_value) & !is.na(patient_value)){
            median_value <- median(syn_week[, cc], na.rm = TRUE)
            Percentile_16 = quantile(syn_week[, cc], probs = 0.16, na.rm = TRUE)
            Percentile_84 = quantile(syn_week[, cc], probs = 0.84, na.rm = TRUE)
            width <- Percentile_84 - Percentile_16
            # what should I do with width == 0 ??!!
            if (width == 0) width <- 1.

            # Calculate the color value based on (patient_value - median_value) / width
            color_value <- (patient_value - median_value)/width
            color_value <- pmin(pmax(color_value, -1), 1)

            # Map color value to the custom palette
            color <- color_ramp(100)[findInterval(color_value, seq(-1, 1, length.out = 100))]
            si29_item_table <- si29_item_table %>%
                tab_style(
                    style = list(
                        cell_borders(
                            sides = c("top", "bottom", "left", "right"),
                            color = color,
                            weight = px(4)
                        )
                    ),
                    locations = list(
                        cells_body(
                            columns = paste(patient_value),
                            rows = cc
                        )
                    )
                )
        }
    }

    # create the legend for the reference population
    legend_dat <- data.frame(t(seq(0, 1, .2)))
    names(legend_dat) <- paste0(seq(0, 100, 20), "%")
    legend <- gt(legend_dat) %>%
        data_color(method = "numeric",
            palette = c("Greys"),
            domain = c(0, 1)) %>%
        fmt_number(pattern = "") %>%
        tab_header(title = "Population Values Legend") %>%
        opt_table_font(font = "Helvetica")

    # create the legend for the patient
    legend_patient_dat <- data.frame(t(seq(-1, 1, .25)))
    names(legend_patient_dat) <- seq(-1, 1, 0.25)
    legend_patient <- gt(legend_patient_dat) %>%
        data_color(method = "numeric",
            palette = custom_palette,
            domain = c(-1, 1)) %>%
        fmt_number(pattern = "") %>%
        tab_header(title = "Patient Values Legend: (patient_value - median)/width") %>%
        opt_table_font(font = "Helvetica")


    return(
        list(
            "table" = si29_item_table,
            "comparison_legend" = legend,
            "patient_legend" = legend_patient
        )
    )

}


create_current_week_summary_bar_chart <- function(){

    # create a summary for each of the columns for all patients as a comparison
    df <- select(syn_week_dat, -c(ID, Week))
    summary_df <- data.frame(
        Median = apply(df, 2, median, na.rm = TRUE),
        Percentile_16 = apply(df, 2, function(x) quantile(x, probs = 0.16, na.rm = TRUE)),
        Percentile_84 = apply(df, 2, function(x) quantile(x, probs = 0.84, na.rm = TRUE))
    )
    # add the symptoms in the correct order
    summary_df$Symptom <- factor(rownames(summary_df), levels = symptoms)

    # create a dataframe for the reference population
    df_long <- pivot_longer(df, cols = symptoms, names_to = "Symptom", values_to = "Value")
    df_long$Symptom <- factor(df_long$Symptom, levels = symptoms)


    # Define a custom color palette
    # custom_palette <- c("#2780E3", "white", "#ff7518")
    custom_palette <- c("#2780E3", "#D3E5F9", "white", "#FFE3D0", "#ff7518")
    custom_palette_gray <- c("white",  "#F5F5F5", "#DCDCDC", "#BEBEBE", "#888888")
    # Create a color ramp function using the custom palette
    color_ramp <- colorRamp(custom_palette)

    # Function to get an interpolated color at a specific value
    get_interpolated_color <- function(value) {
        return(rgb(color_ramp(value), maxColorValue = 255))
    }

    # get the patient data for the bar chart
    p <- select(syn_week_dat[input_params$patient_row, ], -c(ID, Week))
    patient_df <- as.data.frame(t(p))
    names(patient_df) <- c('Value')
    patient_df$Symptom <- factor(rownames(patient_df), levels = symptoms)

    # I wonder if there's a way to get the percentiles without a for loop?
    patient_df$Percentile <- 0
    patient_df$Color <- '#D3D3D3'
    for (s in symptoms){
        val <- patient_df[s,]$Value
        ref <- df[[s]]
        if (!is.nan(val)  & !is.na(val)){
            percentile <- ecdf(ref)
            pct <- percentile(val)
            # fix for scenarios where there every entry is the same
            if (diff(range(ref, na.rm = TRUE)) == 0 & pct == 1) pct <- 0.5
            patient_df[s,]$Percentile <- pct
            patient_df[s,]$Color <- get_interpolated_color(pct)
        }
    }
    summary_df$Value <- patient_df$Value
    summary_df$Percentile <- patient_df$Percentile
    summary_df$Color <- patient_df$Color

    # for labelling (so that I can match the size of the other plot)
    breaks <- seq(0, 100, 20)
    labels <- c("0\n", "20", "40", "60", "80", "100")

    # get the maximum value to define the axis limits
    # max_value <- max(unlist(patient_df[sapply(patient_df, is.numeric)]), na.rm = TRUE)
    max_value <- 100

    main <- ggplot() +
        stat_density(
            data = df_long[(df_long$Symptom != "Total"),],
            aes(x = Symptom, y = Value, fill = after_stat(scaled),),
            geom = "raster",
            position = "identity",
            bounds = c(0,100),
            show.legend = FALSE
        ) +
        scale_fill_gradientn(
            colors = custom_palette_gray,
            values = seq(0,1,by = 1/length(custom_palette_gray)),
        ) +
        new_scale_fill() +
        # geom_errorbar(
        #     data = summary_df[(summary_df$Symptom != "Total"),],
        #     aes(x = Symptom, y = NULL, ymin = Median, ymax = Median), 
        #     width = 1, 
        #     color = "darkgray", 
        #     size = 3
        # ) +
        geom_bar(
            data = patient_df[(summary_df$Symptom != "Total"),],
            aes(x = Symptom, y = Value, fill = Color), 
            stat = "identity", 
            color = "black", 
            width = 0.7,
            size = 1
        ) +
        scale_fill_identity() +   
        scale_x_discrete(expand = c(0,0)) +
        scale_y_continuous("", breaks = breaks, labels = labels, limits = c(0, max_value)) +
        facet_grid(Symptom ~ ., 
            scales = "free_y", 
            switch = "both"
        ) +
        coord_flip() +
        guides(fill = FALSE) +
        theme_bw() +
        xlab("") + 
        theme(
            panel.spacing = unit(0, "lines"),
            strip.text = element_text(size = 0, margin = margin(0,0,0,0)),
            plot.margin = margin(0.7, 0.09, 0.85, 5, "cm"),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
         ) 

    total <- ggplot() +
        stat_density(
            data = df_long[(df_long$Symptom == "Total"),],
            aes(x = Symptom, y = Value, fill = after_stat(scaled),),
            geom = "raster",
            position = "identity",
            bounds = c(0,100),
            show.legend = FALSE
        ) +
        scale_fill_gradientn(
            colors = custom_palette_gray,
            values = seq(0,1,by = 1/length(custom_palette_gray)),
        ) +
        new_scale_fill() +
        # geom_errorbar(
        #     data = summary_df[(summary_df$Symptom == "Total"),],
        #     aes(x = Symptom, y = NULL, ymin = Median, ymax = Median), 
        #     width = 1, 
        #     color = "darkgray", 
        #     size = 3
        # ) +
        geom_bar(
            data = patient_df[(summary_df$Symptom == "Total"),],
            aes(x = Symptom, y = Value, fill = Color), 
            stat = "identity", 
            color = "black", 
            width = 0.7,
            size = 1
        ) +
        scale_fill_identity() +   
        scale_x_discrete(breaks = "", labels = "", expand = c(0,0)) +
        scale_y_continuous("Symptom level", breaks = breaks, labels = labels, limits = c(0, max_value)) +
        facet_grid(Symptom ~ ., 
            scales = "free_y", 
            switch = "both"
        ) +
        coord_flip() +
        guides(fill = FALSE) +
        theme_bw() +
        xlab("") + 
        theme(
            strip.text = element_text(size = 0, margin = margin(0,0,0,0)),
            plot.margin = margin(0., 0.09, 0.25, 5, "cm"),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
         ) 

    g <- plot_grid(main, total, 
        labels = c('Symptom', 'Total'), 
        rel_heights = c(length(symptoms) - 1, 1.4),
        label_y = c(1.01, 1.25),
        label_x = c(0.25,0.37),
        ncol = 1,
        align = "v",
        axis = "b"
    )


    return(g)
}

create_time_series_line_plot <- function(){

    # there may be a more streamlined way to do this, but I don't know it!
    median_values <- syn_long_dat %>%
        group_by(Week) %>%
        summarize(across(-c(ID), median, na.rm = TRUE))
    median_values_t <- median_values %>%
        pivot_longer(cols = -c(Week),
            names_to = "Symptom",
            values_to = "Median")

    Q1_values <- syn_long_dat %>%
        group_by(Week) %>%
        summarize(across(-c(ID), ~ quantile(., 0.16, na.rm = TRUE)))
    Q1_values_t <- Q1_values %>%
        pivot_longer(cols = -c(Week),
            names_to = "Symptom",
            values_to = "Q1")

    Q3_values <- syn_long_dat %>%
        group_by(Week) %>%
        summarize(across(-c(ID), ~ quantile(., 0.84, na.rm = TRUE)))
    Q3_values_t <- Q3_values %>%
        pivot_longer(cols = -c(Week),
            names_to = "Symptom",
            values_to = "Q3")

    # for the reference population
    syn_long_dat_long <- na.omit(pivot_longer(syn_long_dat, cols = c(symptoms), names_to = "Symptom", values_to = "Value"))
    syn_long_dat_long$Symptom <- factor(syn_long_dat_long$Symptom, levels = symptoms)

    # Define a custom color palette
    custom_palette <- c("#2780E3", "#D3E5F9", "white", "#FFE3D0", "#ff7518")
    custom_palette_gray <- c("white",  "#F5F5F5", "#DCDCDC", "#BEBEBE", "#888888")
    # Create a color ramp function using the custom palette
    color_ramp <- colorRamp(custom_palette)

    # Function to get an interpolated color at a specific value
    get_interpolated_color <- function(value) {
        return(rgb(color_ramp(value), maxColorValue = 255))
    }

    # get the patient data for the bar chart
    p <- select(syn_long_dat[syn_long_dat$ID == input_params$patient_id, ], -ID)
    patient_df <- p %>%
        pivot_longer(cols = -c(Week),
            names_to = "Symptom",
            values_to = "Value")

    # I wonder if there's a way to get the percentiles without a for loop?
    patient_df$Percentile <- 0
    patient_df$Color <- '#D3D3D3'
    for (row in 1:nrow(patient_df)) {
        val <- patient_df[row, "Value"][[1]]
        sym <- patient_df[row, "Symptom"][[1]]
        wk <- patient_df[row, "Week"][[1]]
        if (!is.nan(val) & !is.na(val)){
            ref <- syn_long_dat[syn_long_dat$Week == wk, sym]
            percentile <- ecdf(ref)
            pct <- percentile(val)
            # fix for scenarios where there every entry is the same
            if (diff(range(ref, na.rm = TRUE)) == 0 & pct == 1) pct <- 0.5
            patient_df[row, 'Percentile'] <- pct
            patient_df[row, 'Color'] <- get_interpolated_color(pct)
        }
    }

    # set the symptoms as a factor and in the correct order
    patient_df$Symptom <- factor(patient_df$Symptom, levels = symptoms)
    patient_df <- patient_df %>%
        mutate(srt = match(Symptom, symptoms)) %>%
        arrange(srt) %>%
        select(-srt)

    # add the patient info to the merged_df
    merged_df <- merge(median_values_t, Q1_values_t, by = c("Week", "Symptom")) %>%
        merge(Q3_values_t, by = c("Week", "Symptom")) %>%
        merge(patient_df, by = c("Week", "Symptom"))
    merged_df$Symptom <- factor(merged_df$Symptom, levels = symptoms)

    # omit the rows with nan values??
    merged_df_clean_limit_week <- na.omit(merged_df[merged_df$Week <= input_params$patient_week, ])

    # for labelling
    breaks <- seq(0, 24, 4)
    labels <- c("0\n(baseline)", "4", "8", "12", "16", "20", "24")
    labels2 <- c("0", "4", "8", "12", "16", "20", "24")

    # function to calculate custom breaks
    custom_breaks <- function(data, n_breaks = 4, tol = 0.5) {
        # Calculate breaks based on data range
        min_value <- min(data)
        max_value <- max(data)
        breaks <- pretty(c(min_value, max_value), n = n_breaks)
        diff <- breaks[2] - breaks[1]
        top_diff <- max_value - breaks[length(breaks)]
        if (abs(top_diff/diff) > tol) {
            breaks <- breaks[1:(length(breaks) - 1)]
            if (top_diff < 0){
                breaks <- breaks[1:(length(breaks) - 1)]
            }
        }
        return(breaks)
    }

    # Calculate min and max values for each facet so that I can limit the syn_long_dat_long dataframe
    # (this way the y axis scaling is fixed by the patient data and not the reference population)
    limits <- merged_df_clean_limit_week %>%
        group_by(Symptom) %>%
        summarize(min_y = min(Value, na.rm = TRUE), max_y = max(Value, na.rm = TRUE))
    
    for (s in symptoms){
        ind <-  which(syn_long_dat_long$Symptom == s & syn_long_dat_long$Value > limits[limits$Symptom == s, ]$max_y*1.2)
        syn_long_dat_long <- syn_long_dat_long[-ind, ]
    }

    # custom bandwidth for the 2d density, based on the data
    custom_h <- function(data){
        min_value <- min(data, na.rm = TRUE)
        max_value <- max(data, na.rm = TRUE)
        return(c(8, (max_value - min_value)/4.))
    }
    custom_h_values <- list()
    for (s in symptoms){
        if (s != "Total") custom_h_values[[length(custom_h_values) + 1]] = custom_h(merged_df[merged_df$Symptom == s, ]$Value)
    }

    main <- ggplot() +
        stat_density_2d(
            data = syn_long_dat_long[(syn_long_dat_long$Symptom != "Total"),],
            aes(x = Week, y = Value, fill = after_stat(ndensity),),
            geom = "raster",
            position = "identity",
            h = unlist(custom_h_values),
            contour = FALSE,
            show.legend = FALSE
        ) +
        scale_fill_gradientn(
            colors = custom_palette_gray,
            values = seq(0,1,by = 1/length(custom_palette_gray)),
        ) +
        new_scale_fill() +
        # geom_line(
        #     data = merged_df[(merged_df$Symptom != "Total"),],
        #     aes(x = Week, y = Median),
        #     color = "darkgray", 
        #     # linetype = "dashed", 
        #     size = 1.5
        # ) +
        geom_line(
            data = merged_df_clean_limit_week[(merged_df_clean_limit_week$Symptom != "Total"),], 
            aes(x = Week, y = Value)
        ) +
        geom_point(
            data = merged_df_clean_limit_week[(merged_df_clean_limit_week$Symptom != "Total"),], 
            aes(x = Week, y = Value, fill = Color), 
            shape = 21, 
            color = "black", 
            size = 4, 
            stroke = 1.5
        ) + 
        scale_fill_identity() + 
        facet_grid(Symptom ~ ., 
            scales = "free_y", 
            switch = "both",
        ) + 
        scale_x_continuous("", breaks = breaks, labels = labels2, limits = c(0, 24)) + 
        scale_y_continuous("Symptom level", expand = expansion(mult = c(0, 0)),
            breaks = function(x) {
                return(custom_breaks(x))
            },
            position = "right"
        ) +
        expand_limits(x = c(-1, 26)) + 
        ylab("") + 
        # theme_void() + 
        guides(fill = FALSE) +
        theme_bw() + 
        theme(
            panel.spacing = unit(0, "lines"),
            strip.text = element_text(size = 0, margin = margin(0,0,0,0)),
            plot.margin = margin(0.7, 7, 1.2, 0.1, "cm"),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.title.y.right = element_text(margin = margin(l = 10))
        ) 

    h_value <- custom_h(merged_df[merged_df$Symptom == "Total", ]$Value)
    total <- ggplot() +
        stat_density_2d(
            data = syn_long_dat_long[(syn_long_dat_long$Symptom == "Total"),],
            aes(x = Week, y = Value, fill = after_stat(ndensity),),
            geom = "raster",
            h = h_value,
            contour = FALSE,
            show.legend = FALSE
        ) +
        scale_fill_gradientn(
            colors = custom_palette_gray,
            values = seq(0,1,by = 1/length(custom_palette_gray)),
        ) +
        new_scale_fill() +
        # geom_line(
        #     data = merged_df[(merged_df$Symptom == "Total"),],
        #     aes(x = Week, y = Median),
        #     color = "darkgray", 
        #     # linetype = "dashed", 
        #     size = 1.5
        # ) +
        geom_line(
            data = merged_df_clean_limit_week[(merged_df_clean_limit_week$Symptom == "Total"),], 
            aes(x = Week, y = Value)
        ) +
        geom_point(
            data = merged_df_clean_limit_week[(merged_df_clean_limit_week$Symptom == "Total"),], 
            aes(x = Week, y = Value, fill = Color), 
            shape = 21, 
            color = "black", 
            size = 4, 
            stroke = 1.5
        ) + 
        scale_fill_identity() +   
        facet_grid(Symptom ~ ., 
            scales = "free_y", 
            switch = "both",
        ) + 
        scale_x_continuous("Weeks since procedure", breaks = breaks, labels = labels, limits = c(0, 24)) + 
        scale_y_continuous("", expand = expansion(mult = c(0, 0)),
            breaks = function(x) {
                return(custom_breaks(x))
            },
            position = "right"
        ) +
        expand_limits(x = c(-1, 26)) + 
        ylab("") + 
        # theme_void() + 
        guides(fill = FALSE) +
        theme_bw() + 
        theme(
            strip.text = element_text(size = 0, margin = margin(0,0,0,0)),
            plot.margin = margin(0., 7, 0.25, 0.1, "cm"),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.title.y.right = element_text(margin = margin(l = 10))
        ) 

    g <- plot_grid(main, total, 
        rel_heights = c(length(symptoms) - 1, 1.4),
        ncol = 1,
        align = "v",
        axis = "b"
    )

    # create another plot just for the legend (not sure there's a simpler way to do this!)
    breaks <- c(0, 1)
    labels <- c("Below\nreference\npopulation", "Above\nreference\npopulation")
    g_legend <- ggplot() +
        geom_point(
            data = merged_df_clean_limit_week, 
            aes(x = Week, y = Value, fill = Percentile), 
        ) + 
        scale_fill_gradientn(
            colors = custom_palette,
            values = seq(0,1,by = 1/length(custom_palette)),
            limits = c(0,1),
            breaks = breaks,
            labels = labels,
        ) +
        guides(
            fill = guide_colorbar(
                title = "",#Scaled offset from median of reference population",
                title.position = "bottom",
                title.hjust = 0.5,
                title.vjust = 0,
                label.position = "bottom"
            )
        ) + 
        theme_bw() + 
        theme(
            legend.position = "bottom",           
            legend.key.width = unit(1, "cm"),
            legend.title.align = 0.5,
            legend.margin = margin(margin(10,0,0,0,"cm")),
            legend.title = element_text(size = 9), 
            legend.text = element_text(size = 12, color = "#555555")
        )   


    legend <- cowplot::get_legend(g_legend)
    

    return(
        list(
            "plot" = g,
            "legend" = legend
        )
    )
}

annotate_img <- function(img, acolor){
    img <- img  %>%
        # left plot label
        # image_annotate(sprintf('\u2191'), size = 200, color = acolor,
        #     boxcolor = "transparent", degrees = 90, location = "+780+1650") %>%
        image_annotate("Plots on the left show\nyour present symptoms\nin color-filled rectangles.", 
            size = 60, color = acolor, boxcolor = "transparent", degrees = 0, location = "+170+1640", font = 'Times') %>%
        # right plot label
        # image_annotate(sprintf('\u2191'), size = 200, color = acolor,
        #     boxcolor = "transparent", degrees = -90, location = "+2800+1800") %>%
        image_annotate("Plots on the right show\nyour symptoms over time\nin color-filled circles.", 
            size = 60, color = acolor, boxcolor = "transparent", degrees = 0, location = "+2890+1640", font = 'Times')  %>%
        # left plot reference (TODO - link x position to actual total reference value)
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = 30, location = "+960+1780")  %>%
        # image_annotate("Half of the reference population\nhave values inside the gray region", size = 60, color = acolor,
        #     boxcolor = "transparent", degrees = 0, location = "+300+1900", font = 'Times')  %>% 
        image_annotate("The reference population is shown in\ngrascale; darker gray means more patients\nwith that symptom value.", 
            size = 60, color = acolor,  boxcolor = "transparent", degrees = 0, location = "+170+1900", font = 'Times')  %>%        
        # right plot reference (TODO - link x position to actual total reference value)
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = -30, location = "+2460+1850")  %>%
        # image_annotate("Half of the reference population\nhave values inside the gray region", size = 60, color = acolor,
        #     boxcolor = "transparent", degrees = 0, location = "+2580+1900", font = 'Times')  %>%      
        image_annotate("The reference population is shown in\ngrayscale; darker gray means more patients\nwith that symptom value.", 
            size = 60, color = acolor, boxcolor = "transparent", degrees = 0, location = "+2580+1900", font = 'Times')  %>%   
        # left plot explanation (TODO - link x position to actual patient value and automatic text)
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = 210, location = "+1110+1700")  %>%
        image_annotate("Your total score is similar to\nthat of the reference population.", 
            size = 60, color = acolor, boxcolor = "transparent", degrees = 0, location = "+1140+1480", font = 'Times')  %>%
        # left plot explanation (TODO - link x position to actual patient value and automatic text)
        image_annotate(sprintf('\u2191'), size = 200, color = acolor,
            boxcolor = "transparent", degrees = 210, location = "+2330+1750")  %>%
        image_annotate("Your total score has decreased\nsince your last visit.", 
            size = 60, color = acolor, boxcolor = "transparent", degrees = 0, location = "+2330+1480", font = 'Times') 

    return(img) 
}
```



Plots
=====================================   

Row {data-height=800, id="chart1"}
-------------------------------------

### Symptoms Summary for Patient `r params$patient_id` at Week `r params$patient_week`
    
```{r, fig.width = 10, fig.height = 10}
bar_chart <- create_current_week_summary_bar_chart()
line_plot <- create_time_series_line_plot()

g <- plot_grid(bar_chart, line_plot$plot, ncol = 2, align = "h", rel_widths = c(0.49,0.51), axis = "l")
p <- plot_grid(g, line_plot$legend, ncol = 1, rel_heights = c(1, 0.2))

# save the image and then read it back in so that I can annotate it more easily and have consistent sizing!
tmp <- tempfile("image0", fileext = ".png")
ggsave(tmp, p, width = 12, height = 8)
img <- image_read(tmp)

if (params$annotate_plot) img <- annotate_img(img, "#a200aa")

image_trim(img)


```


<!-- 
Row {data-height=125}
-------------------------------------

### Description
The figures above show results from survey(s) you filled out recording the level of your symptoms at each doctor visit.  

The panels on the left show your current symptoms in color-filled rectangles compared to a reference population shown in gray lines. The panels on the right show your symptoms over time in color-filled circles compared to the same reference population shown in gray dashed lines. 

In all panels, the color indicates how your symptom level compares with that of the reference population, with blue being lower and orange being higher than the reference population, as indicated by the colorbar at the bottom.   
-->



Tables
=====================================  

Row {data-width=1050}
-------------------------------------

### Patient Scores Compared to Aggregate for Patient `r params$patient_id` at Week `r params$patient_week` {class="scrollable-table"}

```{r}
tbl <- create_full_table()
tbl$table
tbl$comparison_legend
tbl$patient_legend
```

<!-- used to click on the Tables panel so that I can render it -->
```{r results='asis'}
if (params$show_table) {
  js_code <- '<script>console.log("trying to show table");setTimeout(function() {var tablesPanel = document.querySelector(\'a[href="#tables"]\');tablesPanel.click();}, 100);</script>'
} else {
  js_code <- ''
}
cat(js_code)
```